---
title: "Mass Shooting"
author: "Siyuan Ji", "Sean Park", "Junhan Jiao"
date: "11/14/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


### Chart for Year Injured
```{r}
# Chart for Year Injured
plot(year_table, main = "Chart for Year Injured", type = "l")
```
Looking into the “Chart for year injured” we can see throughout the year 2000 - 2008 there was only a small increase of about 100 total injuries. With a spike around 2009, the number of injuries jumped up to around 170 a year. Coming down all the way to close to zero by 2010. Seeing the visualization more clearly we can see that there was an insane spike around 2014 that shot up all the way to a near 1000 injuries, shooting back down to the later years. 



### Pie chart of Gender
```{r}
pie(slices,labels = lbls, col=rainbow(length(lbls)),
    main="Pie Chart of Gender")
```
As seen on the pie chart there were a total of 719 injuries in the gender column. 
Males: 608 injuries 
Females: 7
males/females: 11
unknown : 93

### Box plot of Victum
```{r}
victim_graph <- ggplot(data = victim_table) +
  geom_col(mapping = aes(x = victum_type, y = victum_number))
victim_graph
```


```{r cars}
View(race_table)
highest_inj <- max(race_table$num_injured)
highest_injured_race <- filter(race_table, num_injured == highest_inj)$Race
```

